A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-20 manuscript.Rmd
revised figure caption

```{r source-rmarkdown, eval = TRUE, echo = FALSE,  fig.cap="Exemplary source of an R Markdown showing a combination of executable R code and English manuscript text. Code is either given in separate chucks (grey background delimited by triple backticks) or inline (single backticks). "}
knitr::include_graphics("Images/rmarkdown.png")
```

>>>>

```{r source-rmarkdown, eval = TRUE, echo = FALSE,  fig.cap="Exemplary excerpt of an R Markdown file showing a combination of executable R code, which will be dynamically rendered to content on document creation, and English manuscript text. Code is either given in separate chunks (shown in grey background delimited by triple backticks) or inline (single backticks). The resulting document is shown in Figure \\ref{fig:rendered-result}. "}
knitr::include_graphics("Images/rmarkdown.png")
```
